### 2025-02-08 short/sections/training.tex
Update training.tex

\begin{cvhonors}
\cvhonor
{KODAQS Data Quality Academy Certificate Program, University of Mannheim} 
{Data quality dimensions, indicators and metrics to assess data quality, tools and data quality, data management procedures, reproducibility} 
{Mannheim, DEU}
{2025}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{KODAQS Data Quality Academy Certificate Program, University of Mannheim} 
{Data quality dimensions, indicators and metrics to assess data quality, tools and data quality, data management procedures and reproducibility} 
{Mannheim, DEU}
{2025}
\end{cvhonors}
